---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)

#loading the data from the csv
logged_data <- read_csv('https://docs.google.com/spreadsheets/u/1/d/e/2PACX-1vTTo_mLevK1Lj3NXGYap7-MOmBd5lhhyOhASQUjjUN8jjbMi5atFOoZGGLkcjPf4PfLBztbqt5IOYBu/pub?output=csv')

#renaming data
latest_data <- logged_data %>% 
  rename(gold = 2, econ_augment = 3)

#finding the mean, max, and number of observations
avg_gold <- round(mean(latest_data$gold, na.rm = TRUE), 1)
max_gold <- max(latest_data$gold, na.rm = TRUE)
game_count <- nrow(latest_data)
```

```{css}
h2 {
  color: #2c3e50;
  font-family: sans-serif;
}

p {
  color: #333333;
  font-family: sans-serif;
}
```

## Recreating a Korean Top 100 TFT Strategy

The purpose of this analysis is to evaluate how viable a top 100 Korean TFT player's stratergy is, where they play high tempo and level to 8 on Stage 4-1 and rolldown all their gold on Stage 4-2.

This report tracks how much gold will be left for the 4-2 rolldown based on whether an econ augment is taken or not. The data I have collected was via a Google Form.

### Key Game Summaries
```{r}
# Using paste() to create comments on the summary values I have created

summary_text_1 <- paste("Across", game_count, "games tracked, my average gold at the 4-2 rolldown is", avg_gold, "g.")
summary_text_2 <- paste("The most gold I have managed to accumulate at this stage is", max_gold, "g.")

print(summary_text_1)
print(summary_text_2)


#chart 1: Frequency of Econ Augments
#this helps me find out how often econ augments are played on this comp and playstyle
latest_data %>% 
  ggplot() +
  geom_bar(aes(x = econ_augment), fill = "#aecdd2") +
  labs(title = "Frequency of Econ Augment Selection",
       subtitle = "Data collected from recent TFT matches",
       caption = "Source: Personal TFT match tracking via Google Forms",
       x = "Took Econ Augment?",
       y = "Number of Games")

#chart 2: Average Gold at 4-2 by Augment Type
#identifying if taking econ augments actually leads to higher gold at 4-2
latest_data %>% 
  ggplot() +
  geom_bar(aes(x = gold, fill = econ_augment)) +
  labs(title = "Econ Augment = more Gold?",
       subtitle = "Comparing gold counts at 4-2 and econ augments from recent TFT matches",
       caption = "Source: Personal TFT match tracking via Google Forms",
       x = "Total Gold at 4-2",
       y = "Number of Games",
       fill = "Econ Augment?")

```
